%% start of file `template.tex'.
%% Copyright 2006-2015 Xavier Danaux (xdanaux@gmail.com).
%
% This work may be distributed and/or modified under the
% conditions of the LaTeX Project Public License version 1.3c,
% available at http://www.latex-project.org/lppl/.

\documentclass[11pt,a4paper,sans]{moderncv}        % possible options include font size ('10pt', '11pt' and '12pt'), paper size ('a4paper', 'letterpaper', 'a5paper', 'legalpaper', 'executivepaper' and 'landscape') and font family ('sans' and 'roman')

% moderncv themes
\moderncvstyle{classic}                             % style options are 'casual' (default), 'classic', 'banking', 'oldstyle' and 'fancy'
\moderncvcolor{burgundy}                               % color options 'black', 'blue' (default), 'burgundy', 'green', 'grey', 'orange', 'purple' and 'red'
%\renewcommand{\familydefault}{\sfdefault}         % to set the default font; use '\sfdefault' for the default sans serif font, '\rmdefault' for the default roman one, or any tex font name
%\nopagenumbers{}                                  % uncomment to suppress automatic page numbering for CVs longer than one page

% character encoding
%\usepackage[utf8]{inputenc}                       % if you are not using xelatex ou lualatex, replace by the encoding you are using
%\usepackage{CJKutf8}                              % if you need to use CJK to typeset your resume in Chinese, Japanese or Korean
%\usepackage{hyperref}

% adjust the page margins
\usepackage[margin=0.75in,scale=1.0]{geometry}
%\setlength{\hintscolumnwidth}{3cm}                % if you want to change the width of the column with the dates
%\setlength{\makecvtitlenamewidth}{10cm}           % for the 'classic' style, if you want to force the width allocated to your name and avoid line breaks. be careful though, the length is normally calculated to avoid any overlap with your personal info; use this at your own typographical risks...

% personal data
\name{Vincent}{Zvikaramba}
%\title{Resumé title}                               % optional, remove / comment the line if not wanted
%\address{street and number}{postcode city}{country}% optional, remove / comment the line if not wanted; the "postcode city" and "country" arguments can be omitted or provided empty
% \phone[mobile]{}                   % optional, remove / comment the line if not wanted; the optional "type" of the phone can be "mobile" (default), "fixed" or "fax"
\email{zvikovincent@gmail.com}                             % optional, remove / comment the line if not wanted
%\homepage{www.johndoe.com}                         % optional, remove / comment the line if not wanted
\social[linkedin]{zvikaram}                        % optional, remove / comment the line if not wanted
%\social[twitter]{phhusson}                             % optional, remove / comment the line if not wanted
\social[github]{vince2678}                              % optional, remove / comment the line if not wanted
%\extrainfo{additional information}                 % optional, remove / comment the line if not wanted
%\photo[64pt][0.4pt]{picture}                       % optional, remove / comment the line if not wanted; '64pt' is the height the picture must be resized to, 0.4pt is the thickness of the frame around it (put it to 0pt for no frame) and 'picture' is the name of the picture file
%\quote{Some quote}                                 % optional, remove / comment the line if not wanted

% bibliography adjustements (only useful if you make citations in your resume, or print a list of publications using BibTeX)
%   to show numerical labels in the bibliography (default is to show no labels)
\makeatletter\renewcommand*{\bibliographyitemlabel}{\@biblabel{\arabic{enumiv}}}\makeatother
%   to redefine the bibliography heading string ("Publications")
%\renewcommand{\refname}{Articles}

% bibliography with mutiple entries
%\usepackage{multibib}
%\newcites{book,misc}{{Books},{Others}}
%----------------------------------------------------------------------------------
%            content
%----------------------------------------------------------------------------------

\begin{document}
%\begin{CJK*}{UTF8}{gbsn}                          % to typeset your resume in Chinese using CJK
%-----       resume       ---------------------------------------------------------
%	\vspace*{-15mm}
\makecvtitle
%	\vspace*{-10mm}

\section{Education}
\cventry{2021}{Honours Bachelor of Science}{University of Toronto}{}{}{Statistics, Computer Science}

\section{Professional Summary}

\cvitem{}{Versatile Software Engineer with expertise in full-stack development, DevOps practices, and system optimization. Skilled in leveraging modern frameworks and tools to deliver innovative solutions, with a proven track record of leading projects, mentoring developers, and integrating advanced AI capabilities into existing platforms.}

\section{Skills}
\cvitem{Programming Languages}{TypeScript/JavaScript, Python, Bash, Java, C/C++, PHP, SQL}
\cvitem{Frameworks and Libraries}{React.js, Spring Boot, Django ORM, SQLAlchemy} %, Guice, Gson}
\cvitem{Tools}{Docker, Git, Node.js, Nginx, Jenkins, Ansible, GitLab CI, Gerrit}
\cvitem{DevOps}{Containerization, CI/CD pipelines}
\cvitem{Other}{CloudFlare API, SELinux, Android Build Systems}

\section{Experience}

\cventry{2022--Present}{Software Engineer}{}{TitanFile Inc}{}{
	\begin{itemize}
\item Reviewed and enhanced code quality through code reviews, improving maintainability and reducing bugs.
\item Collaborated with the DevOps team to migrate legacy systems to containerized environments using Docker.
\item Led development of Microsoft 365 integration in Python and TypeScript using WOPI specification, enabling seamless document editing and viewing.
\item Spearheaded internal hackathon project integrating ChatGPT to optimize user workflows and enhance user experience.
\item Refactored core application views from untyped JavaScript to TypeScript, improving code readability and reliability.
\item Resolved performance bottlenecks in PDF watermarking, reducing memory usage by 20\%.
\item Provided technical onboarding and mentorship for new developers, fostering a collaborative team environment.
	\end{itemize}
}

\cventry{2016--2017}{Teaching Assistant}{Software Tools and Systems Programming}{University of Toronto}{}{
	\begin{itemize}
\item Led programming tutorials, aiding students in debugging assignments and improving their technical skills.
\item Evaluated programming submissions, delivering detailed feedback to guide student improvement.
\item Supported course assessment by proctoring exams and coordinating with faculty for grading.
	\end{itemize}
}
\newpage
%\vspace*{-3mm}
\section{Contracts}
\cventry{2022--2023}{Client Management System}{South-Asian Women's Rights Organization}{Toronto}{}{
	\begin{itemize}
\item Redesigned a legacy CMS using Django backend and React.js frontend, ensuring scalability and maintainability.
\item Implemented a REST API to facilitate secure data exchange between MySQL database and frontend.
	\end{itemize}
}
\cventry{2022-2023}{Website}{Promatec Solutions}{South Africa}{}{
	\begin{itemize}
\item Built a responsive website and email solution in collaboration with another developer.
\item Utilized Docker for streamlined deployment and Gerrit Code Review for team collaboration.
\item Automated DNS record management using a Python script integrated with CloudFlare API.
	\end{itemize}
}

\section{Projects}

\cventry{2015--2019}{\href{https://github.com/Galaxy-MSM8916}{Android Custom ROMs}}{}{}{}{
	\begin{itemize}
        \item Analysing Android system logs to debug  builds and create SELinux security policies
		\item Maintained support for Samsung devices originally running Android versions 4.0 through 6.0, allowing them to run newer Android
        versions up to and including Android 10 (Q)
		\item Maintained kernel code provided by the phone and board OEMs (Samsung, Qualcomm),
backporting upstream security fixes, new kernel features and driver updates to legacy code
		\item Developed user-space android system tools and interposing libraries to provide forward compatibility for newer versions of Android to
proprietary OEM libraries and programs
        \item Went through API documentation to create shim or wrapper libraries to maintain comatibility with proprietary libraries from older versions of Android
		\item Customised and created Makefiles for use with Android's various build systems (Make, Ninja)
		\item Deployed Jenkins for automated builds with Gerrit for code review and collaboration with GIT as the VCS backend
	\end{itemize}
}

\end{document}


%% end of file `template.tex'.
