%% start of file `template.tex'.
%% Copyright 2006-2015 Xavier Danaux (xdanaux@gmail.com).
%
% This work may be distributed and/or modified under the
% conditions of the LaTeX Project Public License version 1.3c,
% available at http://www.latex-project.org/lppl/.

\documentclass[11pt,a4paper,sans]{moderncv}        % possible options include font size ('10pt', '11pt' and '12pt'), paper size ('a4paper', 'letterpaper', 'a5paper', 'legalpaper', 'executivepaper' and 'landscape') and font family ('sans' and 'roman')

% moderncv themes
\moderncvstyle{banking}                             % style options are 'casual' (default), 'classic', 'banking', 'oldstyle' and 'fancy'
\moderncvcolor{grey}                               % color options 'black', 'blue' (default), 'burgundy', 'green', 'grey', 'orange', 'purple' and 'red'
%\renewcommand{\familydefault}{\sfdefault}         % to set the default font; use '\sfdefault' for the default sans serif font, '\rmdefault' for the default roman one, or any tex font name
%\nopagenumbers{}                                  % uncomment to suppress automatic page numbering for CVs longer than one page

% character encoding
%\usepackage[utf8]{inputenc}                       % if you are not using xelatex ou lualatex, replace by the encoding you are using
%\usepackage{CJKutf8}                              % if you need to use CJK to typeset your resume in Chinese, Japanese or Korean
%\usepackage{hyperref}

% adjust the page margins
\usepackage[margin=0.75in,scale=1.0]{geometry}

%\setlength{\hintscolumnwidth}{3cm}                % if you want to change the width of the column with the dates
%\setlength{\makecvtitlenamewidth}{10cm}           % for the 'classic' style, if you want to force the width allocated to your name and avoid line breaks. be careful though, the length is normally calculated to avoid any overlap with your personal info; use this at your own typographical risks...

% personal data
\name{Vincent}{Zvikaramba}
%\title{Resumé title}                               % optional, remove / comment the line if not wanted
%\address{street and number}{postcode city}{country}% optional, remove / comment the line if not wanted; the "postcode city" and "country" arguments can be omitted or provided empty
\phone[mobile]{647-220-0748}                   % optional, remove / comment the line if not wanted; the optional "type" of the phone can be "mobile" (default), "fixed" or "fax"
%\email{zvikovincent@gmail.com}                             % optional, remove / comment the line if not wanted
\email{vincent@zvikaramba.com}                             % optional, remove / comment the line if not wanted
%\homepage{www.johndoe.com}                         % optional, remove / comment the line if not wanted
\social[linkedin]{zvikaram}                        % optional, remove / comment the line if not wanted
%\social[twitter]{phhusson}                             % optional, remove / comment the line if not wanted
\social[github]{vince2678}                              % optional, remove / comment the line if not wanted
%\extrainfo{additional information}                 % optional, remove / comment the line if not wanted
%\photo[64pt][0.4pt]{picture}                       % optional, remove / comment the line if not wanted; '64pt' is the height the picture must be resized to, 0.4pt is the thickness of the frame around it (put it to 0pt for no frame) and 'picture' is the name of the picture file
%\quote{Some quote}                                 % optional, remove / comment the line if not wanted

% bibliography adjustements (only useful if you make citations in your resume, or print a list of publications using BibTeX)
%   to show numerical labels in the bibliography (default is to show no labels)
\makeatletter\renewcommand*{\bibliographyitemlabel}{\@biblabel{\arabic{enumiv}}}\makeatother
%   to redefine the bibliography heading string ("Publications")
%\renewcommand{\refname}{Articles}

% bibliography with mutiple entries
%\usepackage{multibib}
%\newcites{book,misc}{{Books},{Others}}
%----------------------------------------------------------------------------------
%            content
%----------------------------------------------------------------------------------

% Page Footer
%\usepackage{fancyhdr}

%\fancyfoot[C]{\textit{\textcolor{gray}{\tiny{Typeset in \LaTeX}}}}

\begin{document}
    %\begin{CJK*}{UTF8}{gbsn}                          % to typeset your resume in Chinese using CJK
    %-----       resume       ---------------------------------------------------------
    \vspace*{-10mm}
    \makecvtitle
    \vspace*{-10mm}
    
    \section{Professional Summary}
    %Proficient in modern web frameworks, RESTful APIs, and cloud infrastructure,
    \cvitem{}{
        % Full Stack Engineer with extensive experience designing and implementing scalable, user-centric solutions, with a strong focus on delivering seamless user experiences and optimizing system performance.
        % Skilled in translating design concepts into responsive interfaces, improving system performance, and leading collaborative projects. Adept at collaborating across teams, mentoring fellow engineers, and integrating innovative technologies.
        %Full Stack Engineer with a focus on scalable, user-focused solutions and system performance. Skilled in building responsive interfaces, leading projects, mentoring, and integrating new technologies.
        %Adept at collaborating across teams, mentoring fellow developers, and integrating innovative technologies.
        %Full Stack Engineer with a strong background in cross-functional collaboration and delivering robust, end-to-end web solutions.
        %Passionate about knowledge-sharing, mentoring peers, and staying ahead of the curve by experimenting with and implementing cutting-edge technologies.
        %Full Stack Engineer passionate about knowledge-sharing, mentoring peers, and staying ahead of the curve by experimenting with and implementing cutting-edge technologies.
        %
        Highly adaptable Full Stack Engineer with 4 years of professional experience in developing secure, high-performance applications using Python, modern JavaScript and web frameworks.
        \\
        Versed in building stacks from the ground up, leveraging the reliability and flexibility of open-source software and modern containerization to maximize reliability, security, reusability high up-time in micro-service based container systems.
    }
    
    \section{Experience}
    
    \cventry{07/2025 -- Present}{Systems Engineer/Software Developer}{South-Asian Women's Rights Organization}{Toronto, Canada}{Client Management System}{
        \begin{itemize}
            %\item Created mock-ups for 10 views
            \item Orchestrated a comprehensive redesign of the PHP and SQL-based CMS using Django and Python3 for the back-end, complemented by React and Next.JS for routing on the front-end, enhancing scalability and maintainability.
            \begin{itemize}
                \item Designed and implemented database schema and equivalent Django models in third-normal form based on 10 physical forms used for client intakes.
                \item Held weekly sprints with a cross-functional team to track project progress and assign tasks for front-end, back-end and data import work.
                \item Developed REST API with the Django Rest Framework, enabling speedy import/export of thousands of client records within 5 minutes.
            \end{itemize}
            %\item Redesigned PHP and SQL based CMS using Django and Python3 on back-end, and React with Next.JS for routing on the front-end, ensuring future scalability and maintainability.
            %            \item Used Django Rest Framework to build REST API for communication between front-end and Django/MySQL back-end.
            %\item Used Django Rest Framework to build REST API for communication between front-end and back-end.
            %\item Used Celery for task queuing and Redis for thread communication, caching and concurrency locking on the back-end in Django.
        \end{itemize}
    }
    
    \vspace*{+1mm}
    
    \cventry{04/2022-- 06/2025}{Full Stack Engineer}{TitanFile Inc}{Toronto, Canada}{}{
        % \textbf{Intermediate Developer}
        % \textbf{Roles}
        % \begin{itemize}
            %     \item Directly Responsible Individual (DRI) - Infrastructure
            %     \item Lead - MS365 integration development
            %     \item Member - Admin Console Rewrite team
            % \end{itemize}
        %\textbf{Responsibilities}
        %\textbf{Accomplishments}
        %\newline
        \begin{itemize}
            \item Spearheaded the migration of Python from version 3.8 to 3.12 as DRI of Infrastructure, leveraging interpreter optimizations to improve back-end performance by 20\%.
            %\item Optimized GitLab CI jobs as DRI to skip unneeded or unchanged jobs, speeding up testing pipelines by 10\%.
            \item Streamlined GitLab CI jobs as the DRI of DevOps, eliminating unnecessary or unchanged jobs, which sped up testing pipelines by 10\%.
            \item Implemented MS365 integration from inception, enabling seamless document editing, while mitigating technical debt through the adoption of TypeScript in the code-base, creating a template for future front-end development in React and TypeScript.
            \begin{itemize}
                \item Employed Celery for efficient task queuing and Redis for orchestrating thread communication, caching, and concurrency locking within the Django framework.
                \item Updated and modernized file previewer, allowing seamless viewing of and navigation between PDFs, images and Microsoft Office supported document formats.
                \item Translated Figma designs into fully responsive and interactive front-end components using React, TypeScript and CSS, with a focus on code and asset re-usability through usage of standard icon sets such as Font Awesome.
                \item Employed Celery for efficient task queuing and Redis for orchestrating thread communication, caching, and concurrency locking within the Django framework.
                \item On-boarded and mentored three new engineers, directly guiding one to become the DRI for MS365 integration
                development.
            \end{itemize}
            \item Created new React components and views as part of Admin Settings Console rewrite on the front-end, implementing 90\% of views according to requirements within 3 months.
            \begin{itemize}
                \item Implemented React Router routing as part of front-end rewrite, simplifying browser-side navigation.
                \item Leveraged React Context API on the front-end to manage and share state between components, improving the     scalability and maintainability of the application.
                \item Decreased front-end document load times by 200ms, optimizing slow database queries by analyzing MySQL slow query log and unit test times.
            \end{itemize}
            \item Resolved system outages caused by watermarking of large PDF files on the back-end, reducing downtime to within 5\% and decreasing memory usage during PDF processing by 10\%, allowing for error-free and more responsive PDF previewing of large files on the front-end.
            \item Modernized 10 000 lines of ES5 JavaScript and Marionette view code to TypeScript 4.0, ES11 JavaScript and React.js, reducing clutter, improving code readability and minimizing technical debt and reducing the incidence of uncaught bugs in front-end code.
            %\item Updated DocuSign integration to accept JSON web-hooks, increasing security by using more secure XML parser implementation and enforcing future usage of JSON web-hooks, while maintaining compatibility with older XML-based web-hooks for a seamless update.
        \end{itemize}
        %\newline
        %    \textbf{New Grad / Junior Developer}
        %\textbf{Responsibilities}
        %\newline
        %\begin{itemize}
        % {
            %\item Updated Ansible templates for services running on CentOS instances to patch security scanner vulnerabilities, helping adhere to OWASP Top 10 and maintain security compliance scores.
            %\item Participated in code reviews, helping enhance code quality, improving maintainability and reducing bugs by encouraging usage of TypeScript over JavaScript and type hinting in Python.
            %\item Wrote code and handled data with security in mind, ensuring HIIPA and GDPR compliance.
            %\item Collaborated with other DevOps team members to migrate legacy virtual machine based systems to containerized environments using Docker.
            %\item Created and maintained Bash shell and Python scripts to run scheduled jobs or perform back fills and administrative tasks on the back-end.
            %}
        %\textbf{General}
        %\end{itemize}
    }
    
    
    %\newpage
    %%\vspace*{-3mm}
    %%\section{Contracts}
    %\cventry{2021--2023}{Client Management System}{South-Asian Women's Rights Organization (Contract)}{Toronto}{}{
        %	\begin{itemize}
            %\item Redesigned the legacy system using Django and Python3 on back-end and React, Next.JS on the front-end, ensuring future scalability and maintainability.
            %\item Designed and deployed REST APIs to facilitate secure, efficient data exchanges between MySQL database and client interfaces.
            %	\end{itemize}
        %}
    \newpage
    \cventry{02/2021 -- 12/2021}{Systems Engineer/Software Developer}{Promatec Solutions}{Pretoria, South Africa}{}{
        \begin{itemize}
            %\item Built and deployed a responsive containerized web application from scratch using React and TypeScript on the front-end and NodeJS on the back-end in a month.
            %\item Devised highly available, micro-service based container systems by implementing web service and email solutions with AWS ECS.
            \item Delivered a responsive single page application in one month, leveraging React and TypeScript for the front-end and
            NodeJS for the back-end development.
            \item Engineered a secure custom email system with Linux-based open-source mail services, incorporating TLS, DKIM, DMARC, and fail2ban for enhanced security.
            \item Leveraged Docker to optimize deployment workflows and Gerrit Code Review to enhance team collaboration.
            \item Automated website and email solution DNS management through a Python script integrated with the CloudFlare API.
        \end{itemize}
    }
    %  \newpage
    \vspace*{+1mm}
    \cventry{09/2016-- 04/2017}{Teaching Assistant}{University of Toronto}{Toronto, Canada}{Software Tools and Systems Programming}{
        \begin{itemize}
            \item Covered weekly lecture materials and aided students in debugging code assignments during labs of 20 - 30 people, improving students' use of Linux system tools and debuggers such as GDB and Valgrind to identify bugs in code.
            \item Evaluated programming assignment submissions for 50 students over 3 assignments a semester, delivering detailed feedback to guide student improvement.
            \item Supported course assessment by proctoring exams and coordinating with other teaching staff during grading.
        \end{itemize}
    }
    
    \vspace*{+1mm}
    
    \cventry{04/2016-- 12/2020}{Maintainer}{\href{https://github.com/Galaxy-MSM8916}{LineageOS Android Distribution}}{}{}{
        \begin{itemize}
            \item Created and maintained device trees for 6 models of Samsung devices past official security or release update support.
            \begin{itemize}
                \item Implemented shim libraries in C/C++ to allow use of older proprietary vendor modules after Hardware Abstraction Layer (HAL) ABI changes in AOSP, ensuring device compatibility between major Android releases.
                \item Analyzed system logs from Android devices to debug code, identify and fix SELinux security policy issues and ensure fully functionality while maintaining compatibility and security between Android upgrades.
            \end{itemize}
            \item Updated older Linux kernel vendor code to keep up with major changes in AOSP driver interfaces and maintain security and stability.
            \begin{itemize}
                \item Patched 40 CVEs in device kernel code to thwart security bugs as part of LineageOS official build cycles.
                \item Merged board-specific kernel code from CodeAurora Forums (now CodeLinaro), AOSP common, and LineageOS to maintain kernel compatibility and provide security patches with new Android releases.
            \end{itemize}
            \item Configured Jenkins and BuildKite to run builds triggered by GitHub web-hooks.
            \begin{itemize}
                \item Configured both baremetal and cloud-based Debian-based build executors to create test builds weekly and on-demand as required.
                \item Created and maintained Linux shell and Python scripts to perform full Android builds and upload artifacts to cloud storage for distribution on device communities, speeding up the build cycle by 40 minutes.
            \end{itemize}
        \end{itemize}
    }
    \vspace*{+3mm}
    \section{Education}
    \cventry{09/2014 -- 12/2020}{Honors BSc}{University of Toronto}{Statistics and Computer Science}{}{} %{Statistics and Computer Science}
    
    \section{Skills}
    \cvitem{Languages}{Python,TypeScript/JavaScript, SQL, Bash/Unix Shell, Makefile, C/C++, Java}
    %\cvitem{Frameworks}{React, Spring Boot, Django, SQL Alchemy, Guice, Gson, Docker, Git, Node.js, Nginx, Jenkins, Ansible, GitLab CI, Gerrit, MySQL/MariaDB, Redis}
    %\cvitem{Frameworks and Libraries}{React, Spring Boot, Django, SQL Alchemy, Guice, Gson, Docker, Git, Node.js, Nginx, Jenkins, Ansible, GitLab CI, Gerrit, MySQL/MariaDB, Redis}
    %\cvitem{Frameworks and Libraries}{React.JS, Django, Docker, Git, Node.js, Nginx, Ansible, GitLab CI, MySQL/MariaDB, Redis}
    %\cvitem{Front-end}{TypeScript/JavaScript, React.js, Jest, Playwright, Backbone.js, HTML5, SCSS }
    %\cvitem{Back-end}{Python, Django, NPM/Node.js, Docker, Git, Bash/Unix shell scripting, MySQL}
    \cvitem{Technologies}{Docker, PostMan, Ansible, Playwright, NextJS, Jest, Git, GitLab, SE Linux, Jenkins, BuildKite}
    \cvitem{Operating Systems}{Ubuntu/Debian-based distributions, CentOS, Android/AOSP-based systems}
    \cvitem{Other}{Agile/Scrum Methodologies, Android Build Systems}
\end{document}

%% end of file `template.tex'.
